Model

### 2019-04-17 stats/model.Rmd
infer sem knowledge with developmental so param

@@

    // var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
    // var so_int = uniformDrift({a: -2, b: 2, width: 0.2})

@@

      // var speakerOptimality = so_int  + so_slope * age

@@

    return extend([
      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn}
    ])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 1000, burn = 1000, verbose = T)
)

sem_know <- sem_know_model %>%
  select(value) %>%
  map_df(bind_rows)%>%
  rename(sem_int = `0.sem_int`,
         sem_slope = `0.sem_slope`,
         familiar = `0.familiar`)%>%
         #so_int = `0.so_int`,
         #so_slope = `0.so_slope`)%>% 
  gather(parameter, value, -familiar)

@@

data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

>>>>

  var so_slope = uniformDrift({a: -2, b: 2, width: 0.2})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.2})

@@

@@

      var speakerOptimality = so_int  + so_slope * age

@@

    return extend([
      {sem_int: sem_int, sem_slope: sem_slope, familiar: cndtn, so_int: so_int, so_slope: so_slope}
    ])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 900, burn = 300, verbose = T)
)
# 
# saveRDS(sem_know_model, "../saves/sem_know_model.rds")

sem_know_model <- readRDS("../saves/sem_know_model.rds")

sem_know <- sem_know_model %>%
  select(value) %>%
  map_df(bind_rows)%>%
  rename(sem_int = `0.sem_int`,
         sem_slope = `0.sem_slope`,
         familiar = `0.familiar`,
         so_int = `0.so_int`,
         so_slope = `0.so_slope`)%>% 
  gather(parameter, value, -familiar)

@@

data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "loess", se = F, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")
